# Week 7 Short Answer Questions

## Mira Ensley-Field

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(lubridate)
library(stringr)
```

#15.1
1.) Gauss
```{r}
Mira_bday<-mdy("September 28, 1995")
orig1<-"April 30, 1777"
new1<-mdy(orig1)
interval1<-Mira_bday-new1
print(interval1)
```
2.) Turing
```{r}
orig2<-"06-23-1912"
new2<-mdy(orig2)
interval2<-Mira_bday-new2
print(interval2)
```
3.)Bell
```{r}
orig3<-"3 March 1847"
new3<-dmy(orig3)
interval3<-Mira_bday-new3
print(interval3)
```
4.)Armistice of WW1
```{r}
orig4<-"11:00 am on Nov. 11th,1918 at 11:00am"
tweak4<-substring(orig4,13,26)
new4<-mdy(tweak4)
interval4<-Mira_bday-new4
print(interval4)
```
5.) moon!
```{r}
orig5<-"July 20, 1969"
new5<-mdy(orig5)
interval5<-Mira_bday-new5
print(interval5)
```

#15.2

```{r,hide=TRUE,eval=FALSE}
a<-"42,659.30"
b<-"17%"
c<-"Nineteen"
d<-"L100"
e<-"9.8 m/sec"
f<-"9.8 m/s^2"
g<-"6.6206857 x 10^-34 m2 kg / s"
h<-"6.6206857e-34"
i<-"42.659,30"


a1<-as.numeric(a)
b1<-as.numeric(b)
c1<-as.numeric(c)
d1<-as.numeric(d)
e1<-as.numeric(e)
f1<-as.numeric(f)
g1<-as.numeric(g)
h1<-as.numeric(h)
i1<-as.numeric(i)

a2<-tidyr::extract_numeric(a)
b2<-tidyr::extract_numeric(b)
c2<-tidyr::extract_numeric(c)
d2<-tidyr::extract_numeric(d)
e2<-tidyr::extract_numeric(e)
f2<-tidyr::extract_numeric(f)
g2<-tidyr::extract_numeric(g)
h2<-tidyr::extract_numeric(h)
i2<-tidyr::extract_numeric(i)
```

**as.numeric** will work only on h
**extract_numer** will work on a, b, d, e,f, i

#16.1 
1. boy names ending in vowel
```{r}
BabyNames_small<-sample(BabyNames,1000)
```

Making boy name set
```{r}
boy_names<-
  BabyNames %>%
  group_by(name,sex) %>%
  summarise(total=sum(count)) %>%
  group_by(sex) %>%
  spread(key=sex,value=total) %>%
  filter(M>0) 
```

```{r}
vowel_boys<-
  boy_names %>%
  filter(grepl(".{1,10}[aeiouy]{1}$",name)) %>%
  arrange(desc(M))
```
10 most pop names ending in vowel (I include y as vowel):

George	9928	1451408		
Anthony	7010	1391462		
Joshua	4851	1163815		
Timothy	4318	1057538		
Jeffrey	3497	968822		
Gary	3287	897960		
Larry	3560	803236		
Gregory	2861	702805		
Henry	4466	638441		
Jerry	17304	609670	


2. names ending in "joe" or "jo"
```{r}
names<-
  BabyNames %>%
  group_by(name,sex) %>%
  summarise(total=sum(count)) %>%
  group_by(sex) 
```

```{r}
joe_names<-
  names %>%
  filter(grepl("joe$",name)) %>%
  arrange(desc(total))

jo_names<-
  names %>%
  filter(grepl("jo$",name)) %>%
  arrange(desc(total))

all_joes<-rbind(joe_names,jo_names)
``` 

Billyjoe	M	393		
Bobbyjoe	M	89		
Marjoe	M	12		
Billiejoe	F	6		
Maryjoe	F	6		
Johnnyjoe	M	5		
Maryjo	F	6973		
Billiejo	F	1455		
Marijo	F	1275		
Bobbijo	F	1230	
 


#16.2
What would the given regular expression match?

the regular expresion would extract phone-numbers, and it would only extract the numbers (not dashes)


#16.3

The matches will be 2 strings, it can make 55 matches, they refer to state abbreviations and US terriroty abbreviations 

