# Week 3 Project

## Mira Ensley-Field

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

```{r}
ggplot(data = NCHS, aes(x = bmi)) + geom_density(aes(color=sex,fill=TRUE))+ facet_wrap(~pregnant)
```


This is similar to the graph in the html questions page

What mode of graphic is it? (e.g. density plot, scatter plot, bar plot, …)

- density plot

What variables from the respective data tables are involved?

- sex, pregnat, bmi

What role each of those variables plays in the graphic?

- looking at distribution of bmi according to gender and pregnancy status


In Figure 2, why is there no data variable being used for the yy-axis?

- there is only one figure that I can see...?

PLaying with graphs 
```{r}

ggplot(data = NCHS, aes(x = income), title="income distribution by sex and poverty line") + geom_density(aes(color=sex,fill=TRUE))  + geom_vline(xintercept=1,show.legend=TRUE)
```

# Wrangling

Which color diamonds seem to be largest on average (in terms of carats)?
```{r}
largest_diamonds_color<-
  diamonds %>%
  group_by(color) %>%
  summarise(size=mean(carat)) %>%
  arrange(-size)

```
 the "j" color are the largest on average (1.1.6 carats)
 
 
Which clarity of diamonds has the largest average “table” per carat?
```{r}
largest_clarity_table<-
  diamonds %>%
  group_by(clarity) %>%
  summarise(size=mean(table),weight=mean(carat)) %>%
  arrange(-size/weight)

```

#Voting

Using the Minneapolis2013 data table, answer these questions. summarise(), group_by(), and tally() will be useful in answering the questions.

How many cases are there? 80,101
```{r}
nrow(Minneapolis2013)
```

Who were the top 5 candidates in the Second vote selections.

```{r}

top_candidates <-
  Minneapolis2013 %>%
  group_by(Second) %>%
 summarise(seconds=count(Second)) %>%
  arrange(-seconds)

top_five_candidates<-head(top_candidates,6)
```
1       BETSY HODGES   14399

2        DON SAMUELS   14170

3        MARK ANDREW   12757

5 JACKIE CHERRYHOMES    6470

6           BOB FINE   	3751	

How many ballots are marked “undervote” inFirst choice selections? 

834

```{r}
undervote_first <-
  Minneapolis2013 %>%
  group_by(First) %>%
  filter(First == "undervote") %>%
 summarise(votes=count(First)) 

```
Second choice selections? 

10,598

```{r}
undervote_second <-
  Minneapolis2013 %>%
  group_by(Second) %>%
  filter(Second == "undervote") %>%
 summarise(votes=count(Second)) 

```
Third choice selections? 19,210

```{r}
undervote_third <-
  Minneapolis2013 %>%
  group_by(Third) %>%
  filter(Third == "undervote") %>%
 summarise(votes=count(Third)) 

```

What are the top 3 Second vote selections among people who voted for Betsy Hodges as their first choice?

1        MARK ANDREW  8787

2        DON SAMUELS  8743

3 JACKIE CHERRYHOMES  2563


```{r}
besty_supporters<-
  Minneapolis2013 %>%
  filter(First == "BETSY HODGES") %>%
  group_by(Second) %>%
  summarise(votes=count(Second)) %>%
  arrange(-votes)

besty_supporters_top3<-head(besty_supporters,3)
```

Which Precinct had the highest fraction of First vote selections marked as “undervote”? (To calculate the fraction, use mean(First == "undervote") in the argument to summarise().)

  P-05A

```{r}
high_undervote<-
  Minneapolis2013 %>%
  group_by(Precinct) %>%
  summarise(undervotes=count(First =="undervote"), total=count(First)) %>%
  arrange(-undervotes/total)


```

