---
output: html_document
---
# Week 3 Short Answer Questions

## Mira Ensley-Field

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(mosaic)
```
<!-- put your content after this line -->

# Chapter 5

5.1, 5.2

```{r,eval=FALSE}
barGraphHelper(CPS85)

```

```{r,eval=FALSE}



#wage<-CPS85$wage
#sex<-CPS85$sex
bargraph(wage~sex, data=CPS85, main="NW",
        xlab="sex", col=c("darkgrey","grey"),
        legend = rownames(CPS85), beside=TRUE)
```

# Chapter 6

6.5

- b. State and Polling Organization

6.6

- d. glyph=rectangle, attributes=color and text

6.7

- c.

6.8


```{r}
Small<-
  NCHS %>%
  sample_n(size=5000)
```

```{r,eval=FALSE}
scatterGraphHelper(Small)
```



# Chapter 7
7.1
- a.) summarise() and mean()
- b.) summarise() and /
- c.) arrange()
- d.) filter()
- e.) filter()
- f.) select()


7.4 Finding the errors
- a.)  no "" around First

- b.) can't use BabyNames inside group_by, move to line before

- c.) can't use BabyNames inside summarise, move to line before group_by

```{r}
Tmp<-
  BabyNames %>%
  group_by(year,sex) %>%
  summarise(totalBirths=sum(count))

```

```{r}
Total<-
  BabyNames %>%
summarise(num=sum(count))
```

7.5

a.) Output Table A

- filter(sex==F)

- arrange(count,sex)
   
b.) Output Table B

- arrange(sex)

c.) Output Table C

- arrange(-sex,count)

d.) Ouput Table D

- summarise(totalBirhts=sum(count))

e.) Output Table E

- select(name,count)

    
7.7

a.
```{r}
a<-
  BabyNames %>%
    group_by(year,sex) %>%
    summarise(total=sum(count))

```

b.
```{r}
b<-
  ZipGeography%>%
    group_by(State) %>%
    summarise(pop=sum(Population))

```

c.
```{r}
c<-
  Minneapolis2013 %>%
    group_by(First) %>%
    summarise(voteReceived=n())

```

d.
```{r}
d<-
  Minneapolis2013 %>%
    group_by(First) %>%
    summarise(voteReceived=n())

```

7.11

a. you will get the number of female patients and their average age, and the number of male patients and their average age

b. you will get the number of people with different diagnosises

c.  you will get the number of females with different diagnosises  and their average age, and the number ofemales with different diagnosises  and their average age

d. You will get the number and average age of everyone of the same age with a different diagnosis 

e. the number of people with different ages


7.12

1. nrow()

2. names()

3. help() or View()

4. library()

5. group_by

6. group_by() and  sum()