# Week 6 Short Answer Questions

## Mira Ensley-Field

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```

# Chapter 12

# 12.1 : for each sex find the 5 most popular babyNames adding up over all the years

This was used for testing purposes
```{r}
BabyNames_small<-sample(BabyNames,10000,replace=FALSE)
```

```{r}
Popular<-
  BabyNames %>%
  group_by(name,sex) %>%
  summarise(total=sum(count)) %>%
  mutate(the_rank=rank(desc(total))) %>%
  arrange(-total)
```

Top 5 Male Names
- James
- John
- Robert
- Michael
- William

Top 5 Female Names
- Mary
- Elizabeth
- Patricia
- Jennifer
- Linda

#12.2

I couldn't seem to figure out  how to gather into the correct format
```{r}
fraction<-
  BabyNames_small %>%
  group_by(year)  %>%
  summarise(total=sum(count)) %>%
  mutate(frac_in_top_100=(total/2)) %>%
  gather()

  
```

```{r,eval=FALSE}
glyph<-
  PopularCounts %>%
  spread(frac_in_top_100,total) %>%
  mutate(frac_in_top_100 = 'TRUE' / ('True' + 'FALSE'))
```


#12.3

a.) transformation verb: rank

b.) transformation verb: rank

c.) summary function: nrow

d.) summary function: nrow (if leap year, then fewer cases)

e.) neither

f.) summary function: range

g.) neither...probably use lucidate package

h.) summary function

#13.1

1. There are 8 distinct vertices

2. there are 9 edges

#13.2

1. The certices are the letters A,B,C, and D

2. Table 2 shows them correcly

3. Table 1 has incorrect edges...B and C aren't connected and Table 3 is a completey incorrect configuration

#13.3

Table 2

#13.4

1. the size of the letter is mapped to exports

2. pop is mapped to the shape of the gray symbol
