# Week 2 Short Answer Questions

## Mira Ensley-Field

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

# Ch 1: 1.1, 1.2, 1.4, 1.5
1.1 
- Taffy = value (3)
- year= quantitative (2)
- sex = categorical (1)
- name = categorical (1)
- count = quantitative (2)

1.2

- the table columns don't represent one type of data, nor are the data always in the same format
- there is a comma in Lincoln, Abraham but none of the others
- the term length is two numbers and a dash or the word "to" instead they should perhaps be a start date, and end date, and the range as a single number (ie break it into three columns)
- the last column is numeric for two and words "it depends" for a third

1.4

1. the variables in each table are the column headings
- Data Table A: Year, Algeria, Brazil, Columbia
- Data Table B: Country, Y2000, Y2001
- Data Table C: Country, Year, Value

2. 

- Data Table A: a Year
- Data Table B: a Country
- Data Table C: a country in a year

1.5

- there are 5 variables
- each case is a particular flight 

#Ch 2: 2.2, 2.3, 2.4, 2.6, 2.7, 2.8, 2.8, 2.9, 2.10
2.2
- file name, name of argumen in named argument

2.3
- no such data set?
```{r}
library(mosaicData)
data(CPS85,package = "mosaic")
```


2.4
- use = instead of <-
should be...

"```{r,eval=FALSE}
help(NHANES,package-"NHANES")
```""

2.6
- "MyData" name can't start with quotes

- small sample name can't have a space

- .MyData name can't start with period

- sqrt() this is a function, can't be a name


2.7
```{r, eval=FALSE}
data(flights,package="nycflights13")
View(flights)

```
- there are 19 variables

- there are 336776 cases


- a meaning is that one cases is one flight, each row represents a single flight
- Quantitative variables:   "year"           "month"          "day"            "dep_time"       "sched_dep_time"      "dep_delay"      "arr_time"       "sched_arr_time"     "arr_delay    "flight"         "tailnum"             "dest"           "air_time"       "distance"       "hour"           "minute"         "time_hour"   

- Qualitative variables:   "carrier"     "origin"      

2.8

a. 3. improper syntax

b. 3. improper syntax

c. 4. invalid object name

d. 2. unmatched quotes

c. 5. no mistake


2.9

- only "." and "_" can be used (period and underscore)

2.10
- 


#Chapter 3 Questions

##3.1
- data frame: fireplace<- sample_n(Fireplace,size=100)
- function: fireplace(logs,burn = True)
- named arguemnt: cookCalculations<-burn(My_Data_Table, fuel = "fireplace", clients=100)
- variable: fireplace<- My_Data_Table$campfire*10
- 

##3.2
- The statement is missing has the data table (BabyNames) in the wrong spot...in chaining syntax it should be before the %>% and not in the parantheses


##3.3
- should be package=package_name... instead of package<-package_name


##3.4 
1. b.
2. a.
3. c.
4. a.
5. a.
6. c.
7. c.
8. a.
9. b.
10. a.
11. a.
12. a. 
13. a. 
14. d.
15. d.
16. a.
17. d.
18. a.
19. d.


##3.5 
- braintwt is the weight of the brain
- there are 83 cases
- a case is a unique piece of data that has the same underlying attribute
- the levels of vore are carni, herbi, insecti, or omni


##3.6
- c.) is the different one because it is taking a mean, the rest are all doing count

```

##4.1
1. *italic*
2. **bold**
3. #Heading
4.`highlighted`
6. ##Smaller Heading
7.[link](https://xkcd.com/451/)

##4.2
a. need ` not '
b. need ` not "
c. need three ``` at the end not two
d. need new lines for entry
e. need three ``` at the end not four

##4.3


##4.4
1. url
2. file
3. neither
4. url
5. neighter
6. both

##4.5


